---
title: "Homework assignment 4"
author: "Shuhan Song"
date: "November 22, 2019"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
# set global chunk options: images will be 7x5 inches
knitr::opts_chunk$set(fig.width=7, fig.height=5, warning = FALSE, message = FALSE)
options(digits = 4)


## indents are for indenting r code as formatted text
## They may need to be adjusted depending on your OS
# if your output looks odd, increase or decrease indent
indent1 = '    '
indent2 = '        '
indent3 = '            '
```


```{r}
library(tidyverse)
library(tree)
library(randomForest)
library(gbm)
library(ROCR)
library(e1071)
```

##1. Fundamentals of the bootstrap

a. Given a sample of size n, what is the probability that any observation j is not in in a bootstrap sample? Express
your answer as a function of n.

- __$\frac{n}{3}$__

b. Compute the above probability for n = 1000.

- **`r round(1000/3, 2)`**

c. Verify that your calculation is reasonable by resampling the numbers 1 to 1000 with replace and printing the number of missing observations. 

```{r, indent=indent1}
x <- seq(1:1000)

resample <- sample(x, replace = TRUE)

unique_obs <- unique(resample)

n_unique_obs <- length(unique_obs)

n_missing <- 1000 - n_unique_obs
```

- number of missing observations: `r n_missing`

d. Stephen Curry's Field Goal
```{r, indent=indent1}
attempt <- append(rep(1, times = 62), rep(0, times = 64))

bootstrap_estimates <- sapply(1:1000, function(i) mean(sample(attempt, replace = TRUE)))

n <- 126
fg_true_mean <- mean(attempt)
fg_true_var <- fg_true_mean*(1 - fg_true_mean)/n

hist(bootstrap_estimates, 
     freq = FALSE, 
     breaks = 15, 
     main = "Bootstrap estimate of field goal", 
     xlim = c(0, 1))
curve(dnorm(x, mean = fg_true_mean, sd = sqrt(fg_true_var)), 
      add = TRUE, 
      col = "red", 
      lwd = 3)

lower_limit_95_ci <- quantile(bootstrap_estimates, probs = 0.05)
upper_limit_95_ci <- quantile(bootstrap_estimates, probs = 0.95)
``` 

- The 95% bootstrap confidence interval for Stephen Curry’s “true” end-of-season FG%: (`r round(lower_limit_95_ci, 3)*100`%, `r round(upper_limit_95_ci, 3)*100`%)

- I expect Curry's end-of-season field goal percentage to be lower than 49.2% on 11/19 because his real skill might be between 49.2% and 43% where both percentages are extreme values.

##2. Eigenfaces


